---
title: "PSY 8712 Week 8 Project"
author: "MJ Shim"
output: html_document
---

## **Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/mjshim0220/psy8712-week8.git/HEAD).
An interactive web app is available by [clicking this link instead].

## **Script Settings and Resources**
This is the section for setting the working directory, and loading required libraries. 
```{r setup, message=FALSE, warning=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(shiny)
library(ggplot2)
library(readr)
library(tidyverse)
library(DT)
library(weights)
```

## **Data Import and Cleaning**
```{r import DF, message=FALSE, warning=FALSE, echo=FALSE}
week8_tbl<-read.csv("../data/week3.csv") %>% 
  mutate(q5=6-q5) %>% 
  rowwise() %>% 
  mutate(mean_q1_6=mean(q1:q6),
         mean_q8_10=mean(q8:q10))
```
## **Visualization**
The results below show data on Q1-Q6 and feature a scatter plot presenting the mean scores of Q1-Q6 and Q8-Q10. The chart also includes a regression line for analysis.
```{r visualization, echo=FALSE, warning=FALSE, message=FALSE}
v_df<-week8_tbl %>% 
  select(q1:q6)

datatable(v_df)

week8_tbl %>% 
  ggplot(aes(mean_q1_6,mean_q8_10))+
  geom_point()+
  geom_smooth(method="lm", color="purple")+
  labs(x="Average Score of Q1-6", y="Average Score of Q8-10")
```

## **Analysis**
Through the correlation analysis between two mean information variable, I observed a correlation of `r rd(cor(week8_tbl$mean_q1_6, week8_tbl$mean_q8_10), digits=2)`. However, this correlation coefficient is not significant. 
```{r corrr, message=FALSE, warning=FALSE}
cor.test(week8_tbl$mean_q1_6, week8_tbl$mean_q8_10)
```